\documentclass[letterpaper, 10pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins
\pagestyle{empty} % No page numbers
\begin{document}
%----------HEADING----------
\begin{center}
 \textbf{\LARGE SHIM WUESEOP} \\ \vspace{2pt}
 \href{mailto:your@g.skku.edu}{\underline{shimws0806@g.skku.edu}} $|$
 \href{https://github.com/yourid}{\underline{github.com/simson86}}
\end{center}
%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
 % \item[] : same as \item but with no bullet point ([] replaces the bullet symbol with nothing)
 \item[] \textbf{Programming}: C, C++, python% List your programming languages
 \item[] \textbf{Frameworks \& Tools}: Linux, git, VsCode % List your frameworks and tools
 \item[] \textbf{Languages}: Korean, English% List your spoken languages
\end{itemize}
%-----------EXPERIENCE-----------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
 \item[]
 % \hfill : fills the remaining horizontal space, pushing text to the right
 \textbf{Sergent} \hfill April. 2024 -- October. 2025 \\ % e.g. Mar. 2024 -- Present
 \textit{Republic of Korea Army} \hfill \textit{Pocheon, South Korea}
 \begin{itemize}
 \item Operated and maintained tactical communication equipment, ensuring seamless and secure network connectivity during various field training exercises.
 \item Led and mentored a squad of junior soldiers as a Squad Leader, fostering strong discipline, teamwork, and operational readiness within the unit.
 \end{itemize}
 \item[]
 \textbf{Part-time job} \hfill December. 2022 -- February. 2023 \\ % e.g. Mar. 2024 -- Present
 \textit{Organization Name} \hfill \textit{Seoul, Korea}
 \begin{itemize}
 \item Serving meals, and addressing customer needs in a fast-paced dining environment.
 \item Collaborated closely with kitchen and hall staff to ensure rapid table turnover and a seamless dining experience for guests.
 \end{itemize}
\end{itemize}
%-----------SELECTED PROJECTS-----------
% Include: project name, brief description, and your role
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
\item \textbf{Restaurant Listing Web Application (Matzip App)} \hfill [Start Date] -- [End Date]
\begin{itemize}
\item Developed a web-based restaurant recommendation platform using Flask framework and SQLite database.
\item Implemented HTML/CSS templates for the user interface and structured the project directory for efficient routing.
\end{itemize}
\end{itemize}
%-----------HONORS & AWARDS-----------
% Include: awards, certifications, or honors you have
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
\item \textbf{2023 Dean's List} 
\end{itemize}
%-----------EDUCATION-----------
% Include: university name, degree, major, relevant courses, academic accomplishments, etc
\section*{Education}
\hrule
\vspace{4pt}
\begin{itemize}
\item \textbf{Sungkyunkwan University (SKKU)} \hfill Suwon, South Korea \\
\textit{software}  \hfill Mar. 2023 -- Present
\begin{itemize}
\item Relevant Coursework: Algorithm, Data structure, System Programming, Open-Source Software Practice
\item Academic accomplishments : Academic Excellence Scholarship
\end{itemize}
\end{itemize}
%-------------------------------------------
\end{document}